Key Derivation From Noisy Sources With More Errors Than Entropy

### 2014-02-10 trunk/constantRate/ConstCompFuzzExt.tex
notational fixes

@@

We note that for any code, learning a few bits of a codeword does not inform on the remainder of the bits~(the claim is a direct result of \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).

\begin{claim}
\label{cl:many locations ent}
Let $C$ be the uniform distribution over a subset of $\{0,1\}^\ell$, and let $J\subset \{1,\dots,\ell\}$.  Then $\Hav(C | C_{J^c}) =  H_0(C) - |J^c|$.
\end{claim}

@@

\subsection{Obfuscation}
Our construction uses obfuscation for a family of point functions $\mathtt{I} = \{I_w\}_{w \in \zo^*}$ defined as follows:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at most a polynomial number of oracle queries to the function. In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input. Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points. They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.

\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} Let $\mathtt{I}$ be a family of polynomial-size circuits.  A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for $\mathtt{I}$ with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $ I \in \mathtt{I}$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}
For notational convenience, since we only use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
\section{Computational Fuzzy Extractors}
\label{sec:fuzzy extractors}

@@

A computational extractor is the adaption of a randomness extractor to the computational setting.  Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained. We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average-case:
\begin{definition}
Let $\chi$ be a finite set.
A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\section{Tolerating a Constant Fraction of Errors when $\Huse\le 0$}
\label{sec:construction}
For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.  Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
In the computational setting, a ``long enough'' key may be expanded using a computational extractor~(\lemref{lem:cond and cext}).  We therefore focus on building a computational fuzzy conductor with meaningful output entropy.\lnote{where do we talk about running it multiple times if we don't get enough output from one run?} \bnote{nowhere, it was something I realized yesterday.  For second construction it doesn't make much sense, just increase $\ell$ has same effect.} Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

\begin{construction}
\label{cons:first construction}
Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.  Let $\mathcal{O}$ be an obfuscator for the family of point functions $\mathtt{I}_{\mathcal{Z}}$.  Let  $C\subset \zo^\ell$ be an error-correcting code.
We describe $\gen, \rep$ as follows:

@@

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.  By using the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function.  More formally, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols. This restriction on the distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
\begin{cases}
1 & w_j = w_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I$ making at most $q$ queries
\[
\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}
\lnote{stopped going through section 4 here}

@@

\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions for any $q = \poly(n)$ where each $W_j$ is over $\mathcal{Z}$ where $|\mathcal{Z}| = \omega(\poly(n))$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code.  Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for $\mathtt{I}_{\mathcal{Z}}$. Then for $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$ and resulting entropy $\tilde{m} =H_0(C) - \beta$.
\end{theorem}
\begin{proof}
We argue security in~\lemref{lem:security of cons} and correctness in~\lemref{lem:correct of cons}.
\end{proof}

\begin{lemma}
\label{lem:security of cons}
Let all variables be as in \thref{thm:main thm first cons}.  For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{obf}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{lemma}

We give a brief outline of the proof here; the proof is in \apref{app:security of main cons}.
\begin{proof}[Outline]
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $J$ be the set of indices that exists in \defref{def:block guessable}, the distribution $C'$ is defined as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.  We first note that $C'$ has sufficient entropy.  That is, $\Hav(C' |P) =\Hav(C' | C_{J^c} = C'_{J^c}) = H_0(C) - |J^c|$.  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$, since $P$ is a collection of obfuscated programs there exists a simulator, $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}
\end{proof}
We now a argue correctness of \consref{cons:first construction}.
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
Let all variables be as in \thref{thm:main thm first cons}.
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \ell/|\mathcal{Z}| = \ngl(n)$.
\end{lemma}
\begin{proof}
Recall that $c$ contains at most $\ell$ $1$s.  Since $w'$ is chosen independently of the points $r_j$, this probability is the size of each block, that is $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$. Since the $r_j$ are chosen independently, one has,
\[
\Pr[\text{no $1\rightarrow 0$ flips}] \geq 1-\Pr[\text{some }r_j = w_j']\geq 1-\sum_{j=1}^\ell \Pr[r_j = w_j'] \geq 1-\frac{\ell}{|\mathcal{Z}|}.
\]
\end{proof}

Since there are most $t$ locations when $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$:

\begin{lemma}
\label{lem:correct of cons}
Let all variables be as in \thref{thm:main thm first cons}.
For $\dis(w, w')\leq t$ and $(R, P)\leftarrow \gen(w)$
\[
\Pr[\rep( w', P) = R] \geq 1-\left(\frac{\ell}{|\mathcal{Z}|}+\delta_{code}\right).
\]
That is, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|+\delta_{code}$.
\end{lemma}

\textbf{Note: }By using a more structured type of code, the necessary error tolerance may be decreased from $t$ to  $(1/2+\Omega(1))t$ by arguing that roughly half of the mismatches between $w, w'$ occur where $c_j =1$.  This requires a code where most codewords have Hamming weight close to $1/2$.

\subsection{Discussion of \consref{cons:first construction}}
\label{sec:discussion}
To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
\[
\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
\]

@@

@@

\begin{construction}[Sample-then-Obfuscate]
\label{cons:sampling}
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_j$ is over $\mathcal{Z}$. %and $\gamma = \Omega(n)$.  Let $\ell = \omega(\log(n))$ and $\eta = o(\gamma)$ be integer parameters (we will set them later). Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
Let $\eta$ be a parameter, $C\subset\zo^\ell$ be an error-correcting code and $\mathcal{O}$ be an obfuscator for the family of point functions over $\mathtt{I}_{\mathcal{Z}^\eta}$.  Define $\gen, \rep$ as:

@@

\begin{theorem}
\label{thm:sampling}
Let $n$ be a security parameter.
Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.   Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
$\ell = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.  Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
\begin{align*}
t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
\tilde{m} &=H_0(C)\\
\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
\end{align*}
\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$. Don't worry for submission.}
\end{theorem}

@@

\section{Proof of \lemref{lem:cond and cext}}
\label{sec:cond and cext}
\lnote{I need to check this}
\begin{proof}
It suffices to show if there is some distinguisher $D'$ of size $s'$ where
\[\delta^{D'}((\cext(X; U_d), U_d, SS), (U_\kappa, U_d, SS))>\epsilon_{cond}+ \epsilon_{ext}\]
 then there is an distinguisher $D$ of size $s_{cond}$ where for all $Y$ where $\Hav(Y|SS) \geq \tilde{m}$ such that
 \[
 \delta^{D}((X, SS), (Y, SS))\geq \epsilon_{cond}.
 \]
Let $D'$ be such a distinguisher.  That is,
\[
\delta^{D'}(\cext(X, U_d)\times U_d \times SS, U_\kappa\times U_d\times SS)> \epsilon_{ext}+\epsilon_{cond}.
\]
Then define $D$ as follows.  On input $(y, ss)$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, ss)$.  Note that $|D| \approx s' + |\cext| +d= s_{cond}$.  Then we have the following:
\begin{align*}
\delta^{D}((X, SS), (Y, SS))&= \delta^{D'}((\cext(X, U_d), U_d, SS), \cext(Y, U_d), U_d, SS)\\
&\geq \delta^{D'}((\cext(X, U_d), U_d, SS), (U_\kappa\times U_d \times SS)) \\
&- \delta^{D'}((U_\kappa\times U_d \times SS), (\cext(Y, U_d), U_d, SS))\\
&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
\end{align*}
Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
\end{proof}

>>>>

\bigskip

@@

@@

\subsection{Obfuscation}
Our construction uses obfuscation for a family of point functions $\mathtt{I}_n = \{I_w\}_{w \in \zo^n}$ defined as follows:
\[
I_w(x):\begin{cases} 1 & x=w\\0 & \text{otherwise}\end{cases}.
\]
The required notion of obfuscation is virtual grey-box (VGB) introduced in \cite{bitansky2010strong}. This notion is weaker then the standard notion of virtual black-box (\cite{barak2001possibility}), as it allows the simulator to run in unbounded time while making at most a polynomial number of oracle queries to the function. In the following definition we also require that the obfuscation is composable and secure with respect to auxiliary input. Composable auxiliary-input VGB obfuscators for point functions are constructed in \cite[Theorem 6.1]{bitansky2010strong} from the Strong Vector Decision Diffie-Hellman assumption, which is a generalization of the strong DDH assumption of \cite{canetti1997towards} for tuples of points. They can also be constructed by assuming strong properties of cryptographic hash functions~\cite{canetti1997towards}.

\begin{definition}[$\ell$-composable obfuscation VGB obfuscation with auxiliary input \cite{bitansky2010strong}]
\label{def:obf} A PPT algorithm $\mathcal{O}$ is an $\ell$-composable VGB obfuscator for point functions with auxiliary-input if the following conditions are met:
\begin{enumerate}
\item \emph{Functionality:} for every $n$ and $I \in \mathtt{I}_n$, $\mathcal{O}(I)$ is a circuit that computes the same function as $I$.
\item \emph{Virtual grey-box:}  For every PPT adversary $A$ and polynomial $p$, there exists a (possibly inefficient) simulator $S$ and a polynomial $q$ such that for all sufficiently large $n$, any  sequence of circuits $I^1,\dots,I^\ell \in \mathtt{I}_n$, (where $\ell=\poly(n)$) and for all auxiliary inputs $z\in \zo^*$:
\[
|\Pr_{A,\mathcal{O}}[A(z,\mathcal{O}(I^1),\dots,\mathcal{O}(I^\ell)) = 1] - \Pr_{S}[S^{(I^1,\dots,I^\ell)[q(n)]}(z, 1^{|I^1|},\dots,1^{|I^\ell|}) = 1] | < \frac{1}{p(n)} \enspace,
\]
where $(I^1,\dots,I^\ell)[q(n)]$ is an oracle that answers at most $q(n)$ queries, and where every query of the form $(i,x)$ is answered by $I^i(x)$.
\end{enumerate}
\end{definition}
For notational convenience, since we only use point function obfuscation, we denote the oracle provided to the simulator as $I_w(\cdot, \cdot)$ where $w = w_1,..., w_\ell$ is the vector of obfuscated points.
\section{Computational Fuzzy Extractors}
\label{sec:fuzzy extractors}

@@

A computational extractor is the adaption of a randomness extractor to the computational setting.  Any information-theoretic randomness extractor is also a computational extractor; however, unlike information-theoretic extractors, computational extractors can expand their output arbitrarily via pseudorandom generators once a long-enough output is obtained. We adapt the definition of Krawczyk~\cite{krawczyk2010cryptographic} to the average case:
\begin{definition}
Let $\chi$ be a finite set.
A function $\cext: \zo^\ell \times \{0,1\}^d \rightarrow \{0,1\}^\kappa$ a \emph{$(m, \epsilon, s)$-average-case computational extractor} if for all pairs
of random variables $X, Y$ (with $X$ over $\zo^\ell$) such that
$\tilde{H}_\infty(X|Y) \ge m$, we have $\delta^{\mathcal{D}_{s}}((\cext(X; U_d), U_d, Y), U_\kappa\times
U_d \times Y) \le \epsilon$.
\end{definition}

@@

\section{Tolerating a Constant Fraction of Errors when $\Huse\le 0$}
\label{sec:construction}
For the remainder of this work, we consider the Hamming metric over some alphabet $\mathcal{Z}$.  Our goal is to derive strong keys for a large class of sources where $0\ge \Huse = \Hoo(W) - \log|B_t|$.
Our first construction is inspired by the construction of digital lockers from point obfuscation by Canetti and Dakdouk~\cite{canetti2008obfuscating}.

\begin{construction}
\label{cons:first construction}
Let $\mathcal{Z}$ be an alphabet and let $W = W_1,..., W_\ell$ be a distribution over $\mathcal{Z}^\ell$.  Let $\mathcal{O}$ be an obfuscator for point functions with points from $\mathcal{Z}$.  Let  $C\subset \zo^\ell$ be an error-correcting code.
We describe $\gen, \rep$ as follows:

@@

\consref{cons:first construction} is secure if no distinguisher can tell whether it is working with random obfuscations or obfuscations of $W_j$.  By the security of point obfuscation, anything learnable from the obfuscation is learnable from oracle access to the function. Therefore, our construction is secure as long as enough blocks are unpredictable even after adaptive queries to equality oracles for individual symbols. This restriction on the distribution is captured in the following definition.

\begin{definition}
\label{def:block guessable}
Let $I_w (\cdot, \cdot)$ be an oracle that returns \[I_w(j, w_j')=
\begin{cases}
1 & w_j = w_j'\\
0 & \text{otherwise}.
\end{cases}
\]
A source $W = W_1||...|W_\ell$ is a $(q, \alpha, \beta)$-\emph{unguessable block distribution} if there exists a set $J\subset\{1,..., \ell\}$ of size at least $\ell -\beta$ such that for any unbounded adversary $S$ with oracle access to $I_w$ making at most $q$ queries
\[
\forall j\in J, \Hav(W_j |View(S^{I_{W}(\cdot, \cdot)}))\geq \alpha.
\]
\end{definition}

@@

\begin{theorem}
\label{thm:main thm first cons}
Let $n$ be a security parameter. Let $\mathcal{Z}\subseteq \zo^{\omega(\log n)}$ be an alphabet.
Let $\mathcal{W}$ be a family of $(q,\alpha= \omega(\log n),  \beta)$-unguessable block distributions over $\mathcal{Z}^\ell$, for any $q = \poly(n)$.  Furthermore, let $C$ be a $(\neigh_t, \delta_{code})$-code over $\mathcal{Z}^\ell$.  Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs. Then for any $s_{sec} = \poly(n)$ there exists some $\epsilon=\ngl(n)$ such that \consref{cons:first construction} is a $(\mathcal{Z}^\ell, \mathcal{W}, \tilde{m}=H_0(C)-\beta, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta_{code} + \ell/|\mathcal{Z}|$.
\end{theorem}
\begin{proof}
We first argue security in the following Lemma.

\begin{lemma}
\label{lem:security of cons}
Let all variables be as in \thref{thm:main thm first cons}.  For every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}( C | P ) \geq H_0(C) - \beta$.% for $\epsilon' = 2\epsilon_{obf} + (\ell-\beta)2^{-(\alpha - 1)}$.
\end{lemma}

We give a brief outline of the proof here; the proof is in \apref{app:security of main cons}.
\begin{proof}[Outline]
It is sufficient to show that there exists a distribution $C'$ with conditional min-entropy and $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P))\le \ngl(n)$.  Let $J$ be the set of indices that exists according to \defref{def:block guessable}. Define the distribution $C'$ as a uniform codeword conditioned on the values of $C$ and $C'$ being equal on all indices outside of $J$.  We first note that $C'$ has sufficient entropy, because $\Hav(C' |P) = \Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - |J^c|$ (the second step is by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).  It is left to show $\delta^{\mathcal{D}_{s_{sec}}}((C, P), (C', P)) \le \ngl(n)$.
%Define the distribution $X$ as follows:
%\[X_i =
%\begin{cases}
%W_i & C_i = 0\\
%R_i & C_i = 1.
%\end{cases}\]
The outline for the rest of the proof is as follows:
\begin{itemize}
\item Let $D$ be a distinguisher between $(C, P)$ and $(C', P)$. Since $P$ is a collection of obfuscated programs, there exists a simulator $S$~(outputting a single bit), such that $\Pr[D(C, P)=1]$ is close to $\Pr[S^{\mathcal{O}}(C)=1]$.
\item Show that even an unbounded $S$ making a polynomial number of queries to the stored points cannot distinguish between $C$ and $C'$.  That is, $\Delta(S^{\mathcal{O}}(C),S^{\mathcal{O}}(C'))$ is small.
\item By the security of obfuscation, $\Pr[S^{\mathcal{O}}(C')=1]$ is close to $\Pr[D(C', P)=1]$.
\end{itemize}
\end{proof}
We now argue correctness of \consref{cons:first construction}.
We begin by showing that the probability of a single $1\rightarrow 0$ bit flip in $c$ is negligible.
%Most of the effort in showing the correctness of \consref{cons:first construction} is showing that $\dis(w, w')\leq t$ implies $\dis(c, c')\leq t$.  However, we start by justifying our use of unidirectional codes.
\begin{lemma}
\label{lem:no 1 to 0 flips}
Let all variables be as in \thref{thm:main thm first cons}.
The probability of at least one $1\rightarrow 0$ bit flip~(an obfuscation of a random block being interpreted as the obfuscation of the point) is $ \le \ell/|\mathcal{Z}| = \ngl(n)$.
\end{lemma}
\begin{proof}
Consider a coordinate $j$ for which $c_j=1$. Since $w'$ is chosen independently of the points $r_j$, and $r_j$ is uniform, $\Pr[r_j =w_j']  = 1/|\mathcal{Z}|$. The lemma follows by the union bound, since there are at most $\ell$ such coordinates.
\end{proof}

Since there are most $t$ locations for which $w_j\neq w_j'$ there are at most $t$ $0\rightarrow 1$ bit flips in $c$, which the code will correct with probability $1-\delta_{code}$, because $c$ was chosen uniformly.
Therefore, \consref{cons:first construction} is correct with error at most $\ell/|\mathcal{Z}|$.
\end{proof}

\subsection{Discussion of \consref{cons:first construction}}
\label{sec:discussion}
\lnote{I did not check this calculation -- will do}
To show that $\Huse$ can be negative for \consref{cons:first construction}, we first calculate the size of the Hamming ball.  
\[
\log |B_t| = \log \sum_{i=0}^t {\ell \choose i} (|\mathcal{Z}|-1)^i> \log {\ell \choose t} (|\mathcal{Z}|-1)^t =\Theta(t\log |\mathcal{Z}|) + \log {\ell\choose t}
\]

@@

\paragraph{Improvements}  If most codewords have Hamming weight close to $1/2$, we can decrease the error tolerance needed from the code from $t$ to  about $t/2$, because roughly half of the mismatches between $w$ and $w'$ occur where $c_j =1$.

If $\ell$ is not long enough to get a sufficiently long output, the construction can be run multiple times with the same input and independent randomness.

@@

\begin{construction}[Sample-then-Obfuscate]
\label{cons:sampling}
Let $\mathcal{Z}$ be an alphabet, and let $W = W_1,..., W_\gamma$ be a source where each $W_j$ is over $\mathcal{Z}$. %and $\gamma = \Omega(n)$.  Let $\ell = \omega(\log(n))$ and $\eta = o(\gamma)$ be integer parameters (we will set them later). Let $C\subset \zo^\ell$ be a $(\neigh_{t'}, \delta_{code})$.
Let $\eta$ be a parameter, $C\subset\zo^\ell$ be an error-correcting code and $\mathcal{O}$ be an obfuscator for the family of point functions.  Define $\gen, \rep$ as:

@@

\lnote{in prev construction's theorem statement, $\mathcal{Z}$ grows as a function of $n$, and here it doesn't have to, but may. Right now the differences between the two theorems are too subtle to notice. Make theorem statements similar and highlight the differences.}
\begin{theorem}
\label{thm:sampling}
Let $\mathcal{Z}$ be an alphabet.
Let $n$ be a security parameter.
Let $\mathcal{W}$ be the family of $(\alpha = \Omega(1), \beta\leq \gamma(1-\Theta(1)))$-partial block sources over $\mathcal{Z}^\gamma$ where $\gamma = \Omega(n)$.   Let $\eta$ be such that $\eta = \omega(\log n)$ and $\eta = o(\gamma)$,  and $\ell$ be such that $\ell = O(\poly(n))$ and
$\ell = \omega(\log n)$.  Let $C$ be a $(\neigh_{t'}, \delta_{code})$ where $t' = \Theta(\ell)$.
Let $\mathcal{O}$ be an $\ell$-composable VGB obfuscator for point functions with auxiliary inputs. 
  Then for every $s_{sec} = \poly(n)$ there exists some $\epsilon_{sec} = \ngl(n)$ such that \consref{cons:sampling} is a $(\mathcal{Z}^\gamma, \mathcal{W}, \tilde{m}, t)$-computational fuzzy conductor that is $(\epsilon_{sec}, s_{sec})$-hard with error $\delta$ for
\begin{align*}
t&\le \frac{-\log(1-t'/(2\ell))}{2}\frac{\gamma-\eta}{\eta}  = O(\gamma/\eta) = n /\omega(\log n)\\
\tilde{m} &=H_0(C)\\
\delta &= O(\ell/|\mathcal{Z}|+2^{-\ell} +\delta_{code}).
\end{align*}
\bnote{By increasing the size of $\gamma$ we can actually reduce the hit here.  For example if $\gamma = n^c$, then we only get $t \le \gamma / \omega(\log^{1/c} \gamma)$. Don't worry for submission.}
\end{theorem}

@@

\section{Proof of \lemref{lem:cond and cext}}
\label{sec:cond and cext}
\lnote{I need to check this}
\begin{proof}
It suffices to show if there is some distinguisher $D'$ of size $s'$ where
\[\delta^{D'}((\cext(X; U_d), U_d, P'), (U_\kappa, U_d, P'))>\epsilon_{cond}+ \epsilon_{ext}\]
 then there is an distinguisher $D$ of size $s_{cond}$ such that for all $Y$ with $\Hav(Y|P') \geq \tilde{m}$,
 \[
 \delta^{D}((X,P'), (Y, P'))\geq \epsilon_{cond}.
 \]
Let $D'$ be such a distinguisher.  That is,
\[
\delta^{D'}(\cext(X, U_d)\times U_d \times P', U_\kappa\times U_d\times P')> \epsilon_{ext}+\epsilon_{cond}.
\]
Then define $D$ as follows.  On input $(y, p')$ sample $seed\leftarrow U_d$, compute $r\leftarrow \cext(y; seed)$ and output $D(r, seed, p')$.  Note that $|D| \approx s' + |\cext| +d= s_{cond}$.  Then we have the following:
\begin{align*}
\delta^{D}((X, P'), (Y, P'))&= \delta^{D'}((\cext(X, U_d), U_d, P'), \cext(Y, U_d), U_d, P')\\
&\geq \delta^{D'}((\cext(X, U_d), U_d, P'), (U_\kappa\times U_d \times P')) \\
&- \delta^{D'}((U_\kappa\times U_d \times P'), (\cext(Y, U_d), U_d, P'))\\
&>\epsilon_{cond}+\epsilon_{ext}- \epsilon_{ext} = \epsilon_{cond}.
\end{align*}
Where the last line follows by noting that $D'$ is of size at most $s_{ext}$.  Thus $D$ distinguishes $X$ from all $Y$ with sufficient conditional min-entropy.  This is a contradiction.
\end{proof}

\section{Proof of \lemref{lem:security of cons}}
\label{app:security of main cons}
\begin{proof}
\lnote{I need to check this}
Let $\mathcal{O}$ be a $\ell$-composable VGB obfuscator with auxiliary input for point programs over $\mathcal{Z}$.  Let $W$ be a $(q, \alpha = \omega(\log n), \beta)$-unguessable block distribution.  Our goal is to show that for all $s_{sec} = \poly(n)$ there exists $\epsilon_{sec} =\ngl(n)$ such that $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P)\geq H_0(C)- \beta$. % for $\epsilon' = 2\epsilon_{obf} + (\ell - \beta)2^{-(\alpha-1)}$.
Suppose not, that is suppose there is some $s_{sec} = \poly(n)$ such that exists $\epsilon_{sec} = \poly(n)$ and $H^{\hill}_{\epsilon_{sec}, s_{sec}}(C|P) < H_0(C)-\beta$.
By \defref{def:block guessable} there exists a set of indices $J$ such that all blocks within $J$ are unguessable.  Define by $C'$ the distribution of sampling a uniform codeword where all locations outside $J$ are fixed.  Then 
$\Hav(C' | C_{J^c}) \ge \Hoo(C', C_{J^c}) - H_0(C_{J^c})  = H_0(C) - \beta$ (by \cite[Lemma 2.2b]{DBLP:journals/siamcomp/DodisORS08}).

Let $D$ a distinguisher of size at most $s_{sec}$ such that
\[
| \expe[D(C, P)] - \expe[D(C', P)] > \epsilon_{sec} = 1/\poly(n).
\]
Define the distribution $X$ as follows:
\[X_j =
\begin{cases}
W_j & C_j = 0\\
R_j & C_j = 1.
\end{cases}\]  By the security of obfuscation~(\defref{def:obf}), there exists a unbounded time simulator $S$~(making at most $q$ queries) such that
\begin{align}
\label{eq:dist before}
|\expe [D(P_1,..., P_\ell, C)] - \expe [S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|})] |\leq \epsilon_{sec}/3.
\end{align}
We now prove $S$ cannot distinguish between $C$ and $C'$.
\begin{lemma}
\label{lem:sim cannot distinguish}
$\Delta(S^{I_X(\cdot, \cdot)}(C, 1^{\ell \log |Z|}), S^{I_X(\cdot, \cdot)}(C', 1^{\ell \log |Z|})) \le (\ell-\beta) 2^{-(\alpha+1)}$.
\end{lemma}
